---
title: "Crop Prices in Malawi "
author: "Maxwell Mkondiwa"
output:
  flexdashboard::flex_dashboard:
    #theme: paper
    social: menu
    theme: flatly
    #favicon: img/ios7-location-outline.png
    #source_code: embed
    #runtime: shiny
---
```{r setup, include=FALSE}
 rm(list=ls())
# prep workspace
#devtools::install_github("rstudio/crosstalk")
#new_lib_loc <- .libPaths()[2]
#devtools::install_github("dmurdoch/leaflet@crosstalk4")
#devtools::install_github("rstudio/crosstalk")
library(dplyr)  # tidy data manipulation
library(leaflet)  # interative mapping
library(DT)  # interactive tables
library(crosstalk)  # inter-widget interactivity
library(plotly)
#sch <- readRDS("data/gias_sample.RDS")
#library(mapview)
#library(leaflet)
library(ggplot2)
library(sp)
library(spdep)
library(rgdal)
library(DT)
library(dplyr)
library(rio)
library(sf)
library(ggthemes)
#library(leafgl)
#library(leafpop)

#setwd("C:/Users/User/Desktop/RShiny")
#setwd("G:/My Drive/MalawiAgriculturalEquilibriumDisplacementModel/RShinyApp")
#load("sd_mappricesall59.rda")
load("G:/My Drive/MalawiAgriculturalEquilibriumDisplacementModel/RShinyApp/sd_mappricesall2.rda")


```

Interactives {data-icon="ion-stats-bars"}
=====================================  

Column {data-width=400}
-------------------------------------

### About the dashboard

This dashboard is aimed at disseminating AMIS prices by providing a platform for interactive price data visualization. It also allows one to download data into their local drive.

Commodity price data are available at district level for a period from 1988 to 2019 for over five major crops. 

For more information on how to use the dashboard, click on the "How to use" tab on the right. 

This dashboard is a work in progress. We have released it so as to get feedback from potential users. 







### Filters

```{r filters}
# bscols(
#   filter_checkbox(
#     id = "Region",
#     label = "Region",
#     sharedData = sd_dfprices,
#     group = ~Region
#   ))


filter_select(
  id = "DISTRICT",
  label = "District",
  sharedData = sd_dfprices,
  group = ~DISTRICT
)

filter_select(
   id = "crop",
   label = "crop",
   sharedData = sd_dfprices,
   group = ~crop
 )


filter_select(
    id = "year",
    label = "year",
    sharedData = sd_dfprices,
    group = ~year
  )


# bscols(
#   filter_slider(
#     id = "HAs",
#     label = "HAs",
#     sharedData = sd_dfprices,
#     column = ~HAs,
#     step = 1,
#     round = TRUE,
#     sep = "",
#     ticks = FALSE
#   ),
#   filter_slider(
#     id = "year",
#     label = "year",
#     sharedData = sd_dfprices,
#     column = ~year,
#     step = 1,
#     round = TRUE,
#     sep = "",
#     ticks = TRUE
#   )
#  )
```


<!-- ```{js} -->
<!-- function filter_default() { -->
<!--     document.getElementById("crop").getElementsByClassName("selectized")  -->
<!-- [0].selectize.setValue("Cassava", false); -->
<!--  } -->
<!-- window.onload = filter_default; -->
<!-- ``` -->




Column {data-width=400}
-------------------------------------
### Datatable
    
```{r datatable}
  DT::datatable(sd_dfprices,
    filter = "top",  # allows filtering on each column
    extensions = c(
      "Buttons",  # add download buttons, etc
      "Scroller"  # for scrolling down the rows rather than pagination
    ),
    rownames = FALSE,  # remove rownames
    style = "bootstrap",
    class = "compact",
    width = "100%",
    options = list(
      dom = "Blrtip",  # specify content (search box, etc)
      deferRender = TRUE,
      scrollY = 1000,
      scroller = TRUE,
      columnDefs = list(
        list(
          visible = TRUE,
          targets = c(2,3:5)
        )
      ), 
      buttons = list(
        I("colvis"),  # turn columns on and off
        "copy", # copy to clipboard
        "csv",  # download as .csv
        "excel"  # download as .xlsx
      )
    ),
    colnames = c(
      "DISTRICT",
      "V1",
      "crop",
      "Year",
      "Prices",
      "year"
     ))
```




Column {data-width=300}
-------------------------------------
    
### Interactive map
    
```{r map}
  pal <- colorBin(
  palette = "viridis", domain = CropAnnualPricesDistrictYrdata$Prices,
  bins = seq(0, max(CropAnnualPricesDistrictYrdata$Prices, na.rm = TRUE) +100, by = 100))



#pal <- colorQuantile("viridis", NULL, n = 5)

sd_dfprices %>%
 leaflet()%>%
  leaflet::addProviderTiles(providers$OpenStreetMap) %>%
  leaflet::addProviderTiles(providers$Esri.WorldImagery, group="ESRI Satellite",options=leafletOptions(maxNativeZoom=19,maxZoom=100)) %>%
  
  leaflet::addPolygons(data =sd_mapprices,fillColor = ~pal(Prices),
    color = "white",
    fillOpacity = 0.7,group="Prices",
    label = ~Prices,
    highlightOptions = highlightOptions(
    color = "black",
    bringToFront = FALSE))%>%
  
  leaflet::addLegend(
  pal =pal,  values = ~Prices,group="Prices",
  opacity = 0.7, title = "Prices" )%>%

  leaflet::addMeasure() %>%
    
    addLayersControl(baseGroups = c("OpenStreetMap", "ESRI Satellite"),
                    overlayGroups = c("Prices"),
                   options = layersControlOptions(collapsed = TRUE, autoZIndex = FALSE))

```


Price Trends {.storyboard data-icon="fa-info-circle"}
==================================== 

```{r filter2}
bscols(widths = c(5,5),
      filter_select(id         = 'DISTRICT',
                    label      = 'District',
                    sharedData = sd_dfprices,
                    group      = ~DISTRICT,
                    multiple   = TRUE),
      filter_select(id         = 'crop',
                    label      = 'crop',
                    sharedData = sd_dfprices,
                    group      = ~crop,
                    multiple   = TRUE))


```


### Plot price-year-district

```{r scatter2}
#library(d3scatter)
#d3scatter(sd_dfprices, x = ~Yield, y = ~HAs,color = ~Region, x_label = "Yield", y_label = "HAs")

library(plotly)

sd_dfprices %>% 
  plot_ly(x = ~year, y = ~Prices, ids = ~DISTRICT,color=~crop,
          hoverinfo = "text",
          text = ~paste("DISTRICT:", DISTRICT,
                        "<br>Year:", year,
                        "<br>Prices:", Prices)) %>%
  add_lines() %>%
  plotly::layout(xaxis = list(title = "year"), yaxis = list(title = "Prices"),title = list(text = "Prices"))


```



### Scatterplot prices-year-crop


```{r}
#library(d3scatter)
#d3scatter(sd_dfprices, x = ~Yield, y = ~HAs,color = ~Region, x_label = "Yield", y_label = "HAs")

library(plotly)
sd_dfprices %>% 
  plot_ly(x = ~year, y = ~Prices, ids = ~DISTRICT,color=~DISTRICT,
          hoverinfo = "text",
          text = ~paste("DISTRICT:", DISTRICT,
                        "<br>Year:", year,
                        "<br>Prices:", Prices)) %>%
  add_lines() %>%
 plotly::layout(xaxis = list(title = "year"), yaxis = list(title = "Prices"), title = list(text = "Prices"))



```




<!-- Price Distribution {data-orientation=cols data-icon="fa-info-circle"} -->
<!-- ===================================== -->

Price Distribution  {.storyboard data-icon="fa-info-circle"}
==================================== 



```{r select}
bscols(widths = c(6,6),
      filter_select(id         = 'DISTRICT',
                    label      = 'District',
                    sharedData = sd_dfprices,
                    group      = ~DISTRICT,
                    multiple   = TRUE),
      filter_select(id         = 'crop',
                    label      = 'crop',
                    sharedData = sd_dfprices,
                    group      = ~crop,
                    multiple   = TRUE))
```



### By district

```{r boxplot}

sd_dfprices %>% 
  plot_ly(y = ~Prices, ids = ~DISTRICT,color=~crop,
          hoverinfo = "text",
          text = ~paste("DISTRICT:", DISTRICT,
                        "<br>Year:", year,
                        "<br>Prices:", Prices)) %>%
  add_boxplot(x=~DISTRICT) %>%
  plotly::layout(xaxis = list(title = "District"), yaxis = list(title = "Prices"),
         title = list(text = "Prices"))
```

How to use {data-orientation=rows data-icon="fa-info-circle"}
===================================== 

### How to use

#### Filters

You can:

* select one or more regions from the list buttons 
* select one or more districts from the dropdown menu (remove them with your backspace key)
* select one or more crops from the dropdown menu (remove them with your backspace key)
* select one or more years from the dropdown menu (remove them with your backspace key)

#### Interactive map

You can:

* click to grab and drag the map around
* zoom with the '+' and '--' buttons (top-left) or with your mouse's scroll wheel
* click a marker to reveal a popup with information about that district
* click the button showing a broken square (top-left under the zoom options) to select points on the map using a window that's draggable (click and hold the grid icon in the upper left) and resizeable (click and drag the white boxes in each corner)

#### Interactive table

You can:

* filter each column by typing in the boxes under each column header
* sort the columns (ascending and descending) by clicking on the column header
* change which columns are visible by clicking the Column visibility button
* click 'CSV' or 'Excel' to download the filtered data to a .csv file or a .xlsx
* see how many entries remain after filtering in the bottom-left, where it says 'Showing X to Y of Z entries'



